\chapter{List of Publications}

\begin{enumerate}
\item \textit{Mimicking electromagnetically induced transparency in the magneto-optical activity of magnetoplasmonic nanoresonators.}\\ G. Armelles, A. Cebollada, A. Garc\'ia-Mart\'in, M.U. Gonz\'alez, F. Garc\'ia, D. Meneses-Rodr\'iguez, \underline{N. de Sousa}, L.S. Froufe-P\'erez,  Optics Express \textbf{21}, Issue 22, 27356 (2013).

\item \textit{Interaction Effects on the Magneto-optical Response of Magnetoplasmonic Dimers.}\\ \underline{N. de Sousa}, G. Armelles, A. Cebollada, M.U. Gonz\'alez, F. Garc\'ia, D. Meneses-Rodr\'iguez, L.S. Froufe-P\'erez and A. Garc\'ia-Mart\'in, Phys. Rev. B \textbf{89}, 205419 (2014).

\item \textit{Light emission statistics in a 2D Ising lattice.}\\ \underline{N. de Sousa}, J.J. Saenz, A. Garc\'ia-Mart\'in, L.S. Froufe-P\'erez and M. I. Marqu\'es, Phys. Rev. A \textbf{89}, 063830 (2014).

\item \textit{Self-diffusion and dynamic coexistence in confined fluids.}\\ \underline{N. de Sousa}, J.J. Saenz, A. Garc\'ia-Mart\'in, and L. S. Froufe-P\'erez, \textit{Submitted to Physical Review, Letters, arXiv:1401.3710 [cond-mat.stat-mech]}.

\item \textit{Light emission statistics during solid-liquid phase transition in a Lennard-Jones fluid.}\\ \underline{N. de Sousa}, J.J. Saenz, A. Garc\'ia-Mart\'in, and L.S. Froufe-P\'erez, \textit{Submitted to Physical Review Letters}.

\item \textit{Magnetically controlled optical nanoantennae.}\\ \underline{N. de Sousa}, L.S. Froufe-P\'erez and A. Garc\'ia-Mart\'in, \it{Submitted to ACS Photonics}.
\end{enumerate}